Structured and decorated cospans

### 2019-06-15 cospans.tex
changed some notation in Theorem 2.1

@@

@@

together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(b^\prime)$.}

@@

@@

where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composition of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$. For morphisms, the structure functor $U$ is defined as:

@@

(C) edge node[left]{$f$} (C')

@@

is the object $a_1$ in $\mathsf{A}$ and the source of the 2-morphism

@@

@@

$$\iota \colon F(h)(d) \to d^\prime$$
is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly. These structure functors satisfy the equations $$SU(a)=1(a)=TU(a)$$for all objects $a$ of $\mathsf{A}$.

Given two composable horizontal 1-cells $M$ and $N$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (1,-0.5) {$d \in F(b)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,0) {$b^\prime$};
\node (G) at (5,0) {$a_3$};
\node (H) at (4,-0.5) {$d^\prime \in F(b^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F);
\end{tikzpicture}
\]
the composite $N \odot M$ is given by:
\begin{equation}\label{eq:dcospanscomposition}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,1) {$b^\prime$};
\node (E) at (4,0) {$a_3$};
\node (F) at (2,2) {$b+b^\prime$};
\node (G) at (2,3) {$b+_{a_2} b^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node [above] {$i^\prime$} (D)
(E) edge node [above] {$o^\prime$} (D)
(B) edge node [above] {$j$} (F)
(D) edge node [above] {$j^\prime$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge[bend left] node [left] {$\psi j i$} (G)
(E) edge[bend right] node [right] {$\psi j^\prime o^\prime$} (G);
\end{tikzpicture}
\end{equation}
with the corresponding decoration of the apex $\hat{d} \in F(b+_{a_2} b^\prime)$ given by:
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+b^\prime) \xrightarrow{F(\psi)} F(b+_{a_2}b^\prime)$$
where $\psi \colon b + b^\prime \to b+_{a_2} b^\prime$ is the natural map from the coproduct to the pushout and $\phi_{b,b^\prime} \colon F(b) \times F(b^\prime) \to F(b+b^\prime)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$. Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.

@@

\node (J) at (7,0) {$b''$};
\node (K) at (8,0) {$a_4$};
\node (L) at (7,-0.5) {$d_{M_3} \in F(b'')$};

@@

\node (B) at (1.5,0.5) {$(b+_{a_2} b^\prime)+_{a_3} b''$};
\node (C) at (3,0.5) {$a_4$};
\node (C') at (3,-0.5) {$a_4$};
\node (D) at (1.5,-0.5) {$b+_{a_2}(b^\prime +_{a_3} b'')$};
\node (E) at (5.5,0.5) {$d_{(M_1 \odot M_2) \odot M_3} \in F((b+_{a_2} b^\prime)+_{a_3} b'')$};
\node (F) at (5.5,-0.5) {$d_{M_1 \odot (M_2 \odot M_3)} \in F(b+_{a_2} (b^\prime +_{a_3} b''))$};

@@

@@

@@

$$ d_{(M_1 \odot M_2) \odot M_3} \coloneqq 1 \xrightarrow{\zeta_1} F(b+_{a_2} b^\prime) \times F(b'') \xrightarrow{\phi_{b+_{a_2} b^\prime, b''}} F((b+_{a_2}b^\prime) +b'') \xrightarrow{F(j_{b+_{a_2} b^\prime,b''})} F((b+_{a_2} b^\prime)+_{a_3} b'')$$ $$\zeta_1 = d_{M_3} \lambda^{-1} F(j_{b,b^\prime}) \phi_{b,b^\prime} (d_{M_1} \times d_{M_2}) \lambda^{-1}$$

@@

$$ d_{M_1 \odot (M_2 \odot M_3)} \coloneqq 1 \xrightarrow{\zeta_2} F(b) \times F(b^\prime +_{a_3} b'') \xrightarrow{\phi_{b, b^\prime +_{a_3} b''}} F(b+(b^\prime +_{a_3} b'')) \xrightarrow{F(j_{b,b^\prime +_{a_3} b''})} F(b+_{a_2} (b^\prime+_{a_3} b''))$$ $$\zeta_2 = d_{M_1} \lambda^{-1} F(j_{b^\prime,b''}) \phi_{b^\prime,b''} (d_{M_2} \times d_{M_3}) \lambda^{-1}$$
together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \odot M_2) \odot M_3}) \to d_{M_1 \odot (M_2 \odot M_3)}$. Note that the map $a \colon (b+_{a_2} b')+_{a_3}b'' \to b+_{a_2}(b'+_{a_3}b'')$ is the universal map between two colimits of the same diagram. We also have left and right unitors where given a horizontal 1-cell $M$:

@@

if we, say, compose with the identity horizontal 1-cell of $a_2$ on the right:
\node (D) at (1,-0.5) {$d \in F(b)$};
\node (F) at (4,0) {$a_2$};
\node (H) at (4,-0.5) {$!_{a_2} \in F(a_2)$};

@@

where $!_{a_2} = F(!)  \phi \colon 1 \to F(a_2)$ is the trivial decoration on $a_2$, composing these then gives:
\node (B) at (1,0) {$b+_{a_2} a_2$};
\node (D) at (3.5,0) {$d_{M+!_{a_2}} \in F(b +_{a_2} a_2)$};
(A) edge node[above]{$j \psi_b i$} (B)
(C) edge node[above]{$j \psi_{a_2}$} (B);
where $\psi_b \colon b \to b+a_2$ is the natural map into the coproduct and likewise for $\psi_{a_2}$ and $j \colon b+a_2 \to b+_{a_2} a_2$ is the natural map from the coproduct to the pushout. The decoration $d_{M+!_{a_2}} \colon 1 \to F(b+_{a_2} a_2)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M} \times !_{a_2}} F(b) \times F(a_2) \xrightarrow{\phi_{b,a_2}} F(b+a_2) \xrightarrow{F(j_{b,a_2})} F(b+_{a_2} a_2).$$ We then have that the right unitor $R \colon M \odot 1_{a_2} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a_1},r,\id_{a_2})$ from the above composite to $M$:
\node (B) at (1.5,0.5) {$b+_{a_2} a_2$};
\node (C) at (3,0.5) {$a_2$};
\node (C') at (3,-0.5) {$a_2$};
\node (D) at (1.5,-0.5) {$b$};
\node (E) at (4.5,0.5) {$d_{M+!_{a_2}} \in F(b+_{a_2} a_2)$};
\node (F) at (4.5,-0.5) {$d_{M} \in F(b)$};
(A) edge node[above]{$j \psi_b i$} (B)
(C) edge node[above]{$j \psi_{a_2}$} (B)
(A) edge node[left]{$\id_{a_1}$} (A')
(C) edge node[left]{$\id_{a_2}$} (C')

@@

where $r \colon b+_{a_2} a_2 \xrightarrow{\sim} b$ is a universal map together with the isomorphism $\iota_r \colon F(r)(d_{M+!_{a_2}}) \to d_M$. The left unitor is similar. The source and target functor applied to the left and right unitors and associators yield identities. The left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory. Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
\node (F) at (3,-0.5) {$d_{M_2} \in F(b^\prime)$};
\node (G) at (4,0.5) {$a_2$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$a_3$};
\node (G') at (4,-0.5) {$a_2^\prime$};
\node (H') at (5,-0.5) {$c^\prime$};
\node (I') at (6,-0.5) {$a_3^\prime$};
\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
\node (K) at (7,-0.5) {$d_{N_2} \in F(c^\prime)$};
\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(d_{M_1}) \to d_{M_2}$};
\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(d_{N_1}) \to d_{N_2}$};
\node (A'') at (0,-1.5) {$a_1^\prime$};
\node (A''') at (0,-2.5) {$a_1''$};
\node (B'') at (1,-1.5) {$b^\prime$};
\node (C'') at (2,-1.5) {$a_2^\prime$};
\node (C''') at (2,-2.5) {$a_2''$};
\node (D'') at (1,-2.5) {$b''$};
\node (E'') at (3,-1.5) {$d_{M_2} \in F(b^\prime)$};
\node (F'') at (3,-2.5) {$d_{M_3} \in F(b'')$};
\node (G'') at (4,-1.5) {$a_2^\prime$};
\node (H'') at (5,-1.5) {$c^\prime$};
\node (I'') at (6,-1.5) {$a_3^\prime$};
\node (G''') at (4,-2.5) {$a_2''$};
\node (H''') at (5,-2.5) {$c''$};
\node (I''') at (6,-2.5) {$a_3''$};
\node (J'') at (7,-1.5) {$d_{N_2} \in F(b^\prime)$};
\node (K'') at (7,-2.5) {$d_{N_3} \in F(b'')$};
\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(d_{M_2}) \to d_{M_3}$};
\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(d_{N_2}) \to d_{N_3}$};

@@

(I) edge node [left] {$k$} (I')

@@

(C'') edge node[left]{$g^\prime$} (C''')

@@

(I'') edge node [left] {$k^\prime$} (I''')

@@

\node (B) at (1.5,0.5) {$b+_{a_2} c$};
\node (C) at (3,0.5) {$a_3$};
\node (C') at (3,-0.5) {$a_3^\prime$};
\node (D) at (1.5,-0.5) {$b^\prime +_{a_2^\prime} c^\prime$};
\node (E) at (4.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
\node (F) at (4.5,-0.5) {$d_{M_2 \odot N_2} \in F(b^\prime +_{a_2^\prime} c^\prime)$};
\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(d_{M_1 \odot N_1}) \to d_{M_1^\prime \odot N_1^\prime}$};
\node (A'') at (0,-1.5) {$a_1^\prime$};
\node (A''') at (0,-2.5) {$a_1''$};
\node (B'') at (1.5,-1.5) {$b^\prime +_{a_2^\prime} c^\prime$};
\node (C'') at (3,-1.5) {$a_3^\prime$};
\node (C''') at (3,-2.5) {$a_3''$};
\node (D'') at (1.5,-2.5) {$b'' +_{a_2''} c''$};
\node (E'') at (4.5,-1.5) {$d_{M_2 \odot N_2} \in F(b^\prime+_{a_2^\prime} c^\prime)$};
\node (F'') at (4.5,-2.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{M_2 \odot N_2}) \to d_{M_3 \odot N_3}.$};
(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
(C) edge node[above]{$j \psi_{a_3} o_2$} (B)

@@

(C) edge node[left]{$k$} (C')
(A') edge node [above]{$j \psi_{a_1^\prime} i_1^\prime$} (D)
(C') edge node [above]{$j \psi_{a_3^\prime} o_2^\prime$} (D)

@@

(A'') edge node[above]{$j \psi_{a_1^\prime} i_1^\prime$} (B'')
(C'') edge node[above]{$j \psi_{a_3^\prime} o_2^\prime$} (B'')

@@

(C'') edge node[left]{$k^\prime$} (C''')
(A''') edge node [above]{$j \psi_{a_1''} i_1''$} (D'')
(C''') edge node [above]{$j \psi_{a_3''} o_2''$} (D'')

@@

\node (E) at (4.5,0.5) {$F(b)$};

@@

\node (E'') at (7,0.5) {$F(c)$};
\node (E''') at (7,-0.5) {$F(c^\prime)$};
(D) edge node [above] {$d_{M_1}$} (E)
(D) edge node [below] {$d_{M_2}$} (E')

@@

(D') edge node [above] {$d_{N_1}$} (E'')
(D') edge node [below] {$d_{N_2}$} (E''')

@@

\node (E) at (5.5,0.5) {$F(b) \times F(c)$};
\node (E') at (5.5,-0.5) {$F(b^\prime) \times F(c^\prime)$};
\node (B) at (7.5,0.5) {$F(b+c)$};
\node (B') at (7.5,-0.5) {$F(b^\prime + c^\prime)$};
\node (C) at (9.25,0.5) {$F(b+_{a_2} c)$};
\node (C') at (9.25,-0.5) {$F(b^\prime +_{a_2^\prime} c^\prime)$};
(E) edge node [above] {$\phi_{b,c}$} (B)
(E') edge node [above] {$\phi_{b^\prime,c^\prime}$} (B')
(B) edge node [above] {$F(j_{b,c})$} (C)
(B') edge node [above] {$F(j_{b^\prime,c^\prime})$} (C')

@@

(D) edge node [above] {$d_{M_1} \times d_{N_1}$} (E)
(D) edge node [below] {$d_{M_2} \times d_{N_2}$} (E')

@@

where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes. The decorations $d_{M_1 \odot N_1}$ and $d_{M_2 \odot N_2}$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(b' +_{a_2'} c')$.

@@

\node (A') at (0,-0.5) {$a_1''$};
\node (B) at (2,0.5) {$b+_{a_2} c$};
\node (C) at (4,0.5) {$a_3$};
\node (C') at (4,-0.5) {$a_3''$};
\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
(C) edge node[above]{$j \psi_{a_3} o_2$} (B)

@@

(C) edge node[left]{$k^\prime k$} (C')
(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)

@@

\node (A') at (0,-0.5) {$a_1''$};
\node (C') at (2,-0.5) {$a_2''$};
\node (D) at (1,-0.5) {$b''$};
\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
\node (F) at (3,-0.5) {$d_{M_3} \in F(b'')$};
\node (G) at (4,0.5) {$a_2$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$a_3$};
\node (G') at (4,-0.5) {$a_2''$};
\node (H') at (5,-0.5) {$c''$};
\node (I') at (6,-0.5) {$a_3''$};
\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
\node (K) at (7,-0.5) {$d_{N_3} \in F(c'')$};

>>>>

\node (B) at (1,0) {$m$};
\node (D) at (3,0) {$x \in F(m)$};

@@

\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};

@@

together with a morphism $\iota \colon F(h)(m) \to m^\prime$ in $F(m^\prime)$.}

@@

\textbf{Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.}

@@

where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$. For morphisms, the structure functor $U$ is defined as:

@@

(C) edge node[right]{$f$} (C')

@@

is the object $a$ in $\mathsf{A}$ and the source of the 2-morphism

@@

\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$m^\prime$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};

@@

$$\iota \colon F(h)(m) \to m^\prime$$
is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly. These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\mathsf{A}$.

Given two composable horizontal 1-cells $M$ and $N$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$x \in F(m)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,0) {$n$};
\node (G) at (5,0) {$c$};
\node (H) at (4,-0.5) {$y \in F(n)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F);
\end{tikzpicture}
\]
the composite $N \odot M$ is given by:
\begin{equation}\label{eq:dcospanscomposition}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,1) {$n$};
\node (E) at (4,0) {$c$};
\node (F) at (2,2) {$m+n$};
\node (G) at (2,3) {$m+_{b} n$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node [above] {$i^\prime$} (D)
(E) edge node [above] {$o^\prime$} (D)
(B) edge node [above] {$j$} (F)
(D) edge node [above] {$j^\prime$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge[bend left] node [left] {$\psi j i$} (G)
(E) edge[bend right] node [right] {$\psi j^\prime o^\prime$} (G);
\end{tikzpicture}
\end{equation}
with the corresponding decoration of the apex $x \odot y \in F(m+_{b} n)$ given by:
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
where $\psi \colon m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \colon F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$. Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.

@@

\node (B) at (1,0) {$m_1$};
\node (D) at (1,-0.5) {$x \in F(m_1)$};
\node (F) at (4,0) {$m_2$};
\node (G) at (5,0) {$c$};
\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
\node (I) at (6,0) {$c$};
\node (J) at (7,0) {$m_3$};
\node (K) at (8,0) {$d$};
\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};

@@

\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
\node (C) at (3,0.5) {$d$};
\node (C') at (3,-0.5) {$d$};
\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
\node (E) at (5.5,0.5) {$(x \odot y) \odot z \in F((m_1+_{b} m_2)+_{c} m_3)$};
\node (F) at (5.5,-0.5) {$x \odot (y \odot z) \in F(m_1+_{b} (m_2 +_{c} m_3))$};

@@

(A) edge node[left]{$\id_a$} (A')
(C) edge node[right]{$\id_d$} (C')

@@

(B) edge node [left] {$\sigma$} (D);

@@

$$ (x \odot y) \odot z \coloneqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$

@@

$$ x \odot (y \odot z) \coloneqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
together with the isomorphism $\iota_\sigma \colon F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$. Note that the map $\sigma \colon (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram. We also have left and right unitors where given a horizontal 1-cell $M$:
\node (B) at (1,0) {$m$};
\node (D) at (3,0) {$x \in F(m)$};

@@

if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
\node (B) at (1,0) {$m$};
\node (D) at (1,-0.5) {$x \in F(m)$};
\node (H) at (4,-0.5) {$!_{b} \in F(b)$};

@@

where $!_{b} = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
\node (B) at (1,0) {$m+_{b} b$};
\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
(A) edge node[above]{$j \psi_m i$} (B)
(C) edge node[above]{$j \psi_{b}$} (B);
where $\psi_m \colon m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \colon m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout. The decoration $x \odot !_b \colon 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \colon M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$m+_{b} b$};
\node (C') at (3,-0.5) {$b$};
\node (D) at (1.5,-0.5) {$m$};
\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
\node (F) at (4.5,-0.5) {$x \in F(m)$};
(A) edge node[above]{$j \psi_m i$} (B)
(C) edge node[above]{$j \psi_{b}$} (B)
(A) edge node[left]{$\id_{a}$} (A')
(C) edge node[right]{$\id_{b}$} (C')

@@

where $r \colon m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \colon F(r)(x \odot !_b) \to x$. The left unitor is similar. The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory. Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$m^\prime$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m^\prime)$};
\node (G) at (4,0.5) {$b$};
\node (H) at (5,0.5) {$n$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$b^\prime$};
\node (H') at (5,-0.5) {$n^\prime$};
\node (I') at (6,-0.5) {$c^\prime$};
\node (J) at (7,0.5) {$y \in F(n)$};
\node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(x) \to x'$};
\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(y) \to y'$};
\node (B'') at (1,-1.5) {$m^\prime$};
\node (C'') at (2,-1.5) {$b^\prime$};
\node (C''') at (2,-2.5) {$b''$};
\node (D'') at (1,-2.5) {$m''$};
\node (E'') at (3,-1.5) {$x' \in F(m^\prime)$};
\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
\node (G'') at (4,-1.5) {$b^\prime$};
\node (H'') at (5,-1.5) {$n^\prime$};
\node (I'') at (6,-1.5) {$c^\prime$};
\node (G''') at (4,-2.5) {$b''$};
\node (H''') at (5,-2.5) {$n''$};
\node (I''') at (6,-2.5) {$c''$};
\node (J'') at (7,-1.5) {$y' \in F(n^\prime)$};
\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(x') \to x''$};
\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(y') \to y''$};

@@

(I) edge node [right] {$k$} (I')

@@

@@

(I'') edge node [right] {$k^\prime$} (I''')

@@

\node (B) at (1.5,0.5) {$m+_{b} n$};
\node (C) at (3,0.5) {$c$};
\node (C') at (3,-0.5) {$c^\prime$};
\node (D) at (1.5,-0.5) {$m' +_{b'} n^\prime$};
\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
\node (B'') at (1.5,-1.5) {$m^\prime +_{b\prime} n^\prime$};
\node (C'') at (3,-1.5) {$c^\prime$};
\node (C''') at (3,-2.5) {$c''$};
\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m^\prime+_{b^\prime} n^\prime)$};
\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
(A) edge node[above]{$j \psi_{m} i_1$} (B)
(C) edge node[above]{$j \psi_{n} o_2$} (B)

@@

(C) edge node[right]{$k$} (C')
(A') edge node [above]{$j \psi_{m^\prime} i_1^\prime$} (D)
(C') edge node [above]{$j \psi_{n^\prime} o_2^\prime$} (D)

@@

(A'') edge node[above]{$j \psi_{m^\prime} i_1^\prime$} (B'')
(C'') edge node[above]{$j \psi_{n^\prime} o_2^\prime$} (B'')

@@

(C'') edge node[right]{$k^\prime$} (C''')
(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')

@@

\node (E) at (4.5,0.5) {$F(m)$};
\node (E') at (4.5,-0.5) {$F(m^\prime)$};

@@

\node (E'') at (7,0.5) {$F(n)$};
\node (E''') at (7,-0.5) {$F(n^\prime)$};
(D) edge node [above] {$x$} (E)
(D) edge node [below] {$x'$} (E')

@@

(D') edge node [above] {$y$} (E'')
(D') edge node [below] {$y'$} (E''')

@@

\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
\node (E') at (5.5,-0.5) {$F(m^\prime) \times F(n^\prime)$};
\node (B) at (7.5,0.5) {$F(m+n)$};
\node (B') at (7.5,-0.5) {$F(m^\prime + n^\prime)$};
\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
\node (C') at (9.25,-0.5) {$F(m^\prime +_{b^\prime} n^\prime)$};
(E) edge node [above] {$\phi_{m,n}$} (B)
(E') edge node [above] {$\phi_{m^\prime,n^\prime}$} (B')
(B) edge node [above] {$F(j_{m,n})$} (C)
(B') edge node [above] {$F(j_{m^\prime,n^\prime})$} (C')

@@

(D) edge node [above] {$x \times y$} (E)
(D) edge node [below] {$x' \times y'$} (E')

@@

where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes. The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.

@@

\node (B) at (2,0.5) {$m+_{b} n$};
\node (C) at (4,0.5) {$c$};
\node (C') at (4,-0.5) {$c''$};
\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
(A) edge node[above]{$j \psi_{m} i_1$} (B)
(C) edge node[above]{$j \psi_{n} o_2$} (B)

@@

(C) edge node[right]{$k^\prime k$} (C')
(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
(C') edge node [above]{$j \psi_{n''} o_2''$} (D)

@@

\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b''$};
\node (D) at (1,-0.5) {$m''$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x'' \in F(m'')$};
\node (G) at (4,0.5) {$b$};
\node (H) at (5,0.5) {$n$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$b''$};
\node (H') at (5,-0.5) {$n''$};
\node (I') at (6,-0.5) {$c''$};
\node (J) at (7,0.5) {$y \in F(n)$};
\node (K) at (7,-0.5) {$y'' \in F(n'')$};
\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(x) \to x''$};
\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(y) \to y''$};
